---
title: "Lab 6: The Building Blocks of Inference"
output: html_notebook
---

### Exercise 1

```{r}
library(tidyverse)
library(oilabs)
library(infer)
```

```{r}
data(promote)

sum_promote <-
promote %>% group_by(sex) %>%
  summarize(promo_prop = sum(decision == "promote") / n())

```

$$H_0=$$ male and female has the same mean promotion rate

```{r}
null_promote <-
promote  %>% 
specify(response = decision, explanatory = sex, success = "promote") %>%
hypothesize(decision ~ sex, null = "independence") %>%
generate(rep = 10000, type = "permute") %>% 
calculate(stat = "diff in props", order = c("male", "female"))

null_promote %>% visualize()


null_promote %>% get_p_value(0.2916667, "both")
```

### Exercise 2
$$H_0=$$ 50% of millenials favor same-sex marriage

```{r}
data("millenials")
millenials %>% 
summarise(prop = sum(response == "favor") / n())
```
```{r}
null_millenials <-
millenials %>%
specify(response = response, success = "favor") %>%
hypothesize(null = "point", p = 0.5) %>%
generate(rep = 10000, type = "simulate")%>%
calculate(stat = "prop") 

null_millenials %>% visualize()

null_millenials %>% get_p_value(0.6666667, direction = "both")
```

### Exercise 3
$$H_0=$$ Curry's score rate of long distance shots is 15%, quadruple the average of NBA players that season.
```{r}
data("curry")

sum_curry <- curry %>% summarize(score_rate = sum(shot == "hit") / n())
```

```{r}
null_curry <-
  curry %>% 
  specify(response = shot, success = "hit") %>%
  hypothesize(null = "point", p = 0.3) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop")

null_curry %>% visualize()

null_curry %>% get_p_value(0.48, "both")
```

### Exercise 4
As shown above

### Exercise 5
All of the distributions generated share some similarities with a normal distribution. promote shows a symmetrical bell curve except for the center bin. millenial has an almost symmetrical distribution with tails, and curry shows a one-sidedly trimmed bell curve due to the constraint x >= 0.

### Exercise 6
```{r}
data("survey141")

survey141 <- survey141 %>% filter(computer == "Mac" | computer == "PC")
```

```{r}
survey141 %>% group_by(coffee_tea) %>% summarize(mac_prop = sum(computer == "Mac") / n())
```
$$H_0=$$
The preference to use mac is independent of one's preference to tea or coffee
```{r}
null_survey141 <- 
  survey141 %>%
  specify(response = computer, explanatory = coffee_tea, success = "Mac") %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props", order = c("Tea", "Coffee"))

null_survey141 %>% visualize()

null_survey141 %>% get_p_value(0.6086957 - 0.6538462, direction = "less")
```

