---
title: "Data Wrangling"
output: html_notebook
---
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(oilabs)
library(lubridate)
data(pnwflights)
```

### Exercise 1
```{r}
#dep_delay_hist <- ggplot(pnwflights, aes(x = dep_delay)) + geom_bar()
hist(pnwflights$dep_delay, breaks = c(-100, 0, 5, 100, 200, 300, 400, 500, 2000), right = F)
```
The graph is skewed to the right the only mode interval t is 0 <= t < 5 of departure delay, which means most flight departs on time. Also a considerate amount of flights depart early.


### Exercise 2
```{r}
pnwflights <- pnwflights %>% mutate(avg_speed = distance / air_time * 60)

avg_speed_vs_distance_scatter <- ggplot(pnwflights, aes(y = avg_speed, x = distance)) + geom_point()
avg_speed_vs_distance_scatter
```


### Exercise 3
```{r}
# proportion of flights from pdx
n_origins <- nrow(pnwflights)
pdxflights <- filter(pnwflights, origin == "PDX")
n_pdx <- nrow(pdxflights)
pdx_prop <- n_pdx / n_origins

pop_dest <- pdxflights %>% group_by(dest)
pop_dest <- pop_dest %>% summarise(times = n())
pop_dest[order(pop_dest$times, decreasing = T), ]
```

As in the graph the most frequent destination from Portland is Los Angeles

### Exercise 4
```{r}
delays <- pnwflights %>% group_by(carrier)
delays <- summarise(delays, median = median(dep_delay, na.rm = T), IQR = IQR(dep_delay, na.rm = T))
delays[order(delays$IQR),]
```
As in the dataframe, HA has the least variable departure delays.

### Exercise 5
```{r}
best_flights <-
pnwflights %>% filter(dest == "SFO", origin == "PDX") %>% 
mutate(day_of_week = wday(ymd(paste(year, month, day, sep = "-")), label = T)) %>% 
group_by(day_of_week) %>% 
summarize(total_delay = mean(dep_delay + arr_delay, na.rm = T))
best_flights[order(best_flights$total_delay),]
```
If we consider the least delay for flights as best, we should fly on Wednesday.

### Exercise 6
```{r}
on_time_props <-
pnwflights %>% mutate(on_time = dep_delay < 5) %>%
  group_by(month) %>% 
  summarize(on_time_prop = sum(on_time, na.rm = T) / n())
on_time_props[order(on_time_props$on_time_prop, decreasing = T),]
```

### Exercise 7
```{r}
delay_vs_dist <-
pnwflights %>% group_by(tailnum) %>% 
summarize(avg_delay = mean(arr_delay), avg_dist = mean(distance), n = n()) %>%
filter(n > 20, avg_dist < 2000)
delay_vs_dist
```

```{r}
dvd_plot <- delay_vs_dist %>% ggplot(aes(x = avg_dist, y = avg_delay, size = n)) + geom_point(alpha = .1)
dvd_plot
```



